### 2017-08-07 Paper01_EnthalpyAndCrystallization.tex
Results - Fragility - Cleaned up final paragraph of section. Other minor edits.

\subsubsection{\Acrlong{m}}

Using the isochronic \acrshort{dsc} data the \gls{m} of the \MgZnCa~ system could be established for both the bulk and film. Numerical solutions where used to fit the \gls{vft} relationship for \gls{ht} \cite{Busch1998}.

@@

For the bulk it was found $\beta^{-1} = 1.338E - 16e^{5274 (\frac{1}{T-T_{0}})}$ with Adj. $R^{2}=0.972$, giving a $D^{*}=20.4$, and a \acrlong{m} $m=44.9$. For the film $\beta^{-1} = 5.921E - 11e^{2766 (\frac{1}{T-T_{0}})}$ with Adj. $R^{2}=0.861$, giving a $D^{*}=10.0$, and \acrlong{m} $m=75.0$. See Figure \ref{fig:Fragility_BulkFilm_mValue}.

>>>>

\subsubsection{Fragility}

Using the isochronic \acrshort{dsc} data the \gls{m} of the \MgZnCa~ system could be established for both the bulk and film. Numerical solutions where used to fit the \acrshort{dsc} variant of the \gls{vft} relationship for \gls{ht} \cite{Busch1998}.

@@

Using these two equations for the bulk it was found $\beta^{-1} = 1.338E - 16e^{5274 (\frac{1}{T-T_{0}})}$ with an Adj. $R^{2}=0.972$. This gave a $D^{*}=20.4$, and a \gls{m}$=44.9$. The film was fitted to $\beta^{-1} = 5.921E - 11e^{2766 (\frac{1}{T-T_{0}})}$ with a lower confidence of Adj. $R^{2}=0.861$, likely owing to the reduced number of data points. This gave a $D^{*}=10.0$, and \gls{m}$=75.0$, see Figure \ref{fig:Fragility_BulkFilm_mValue}.
